{\Large\sc Journal Publications}
\vspace{-3mm}
\begin{itemize}
\item {\bf Kenshi Takayama}. {\it Dual Sheet Meshing: An Interactive Approach to Robust Hexahedralization}. Computer Graphics Forum, 38(2) (proceedings of Eurographics), pp.37--48, 2019.
\item Giorgio Marcias, {\bf Kenshi Takayama}, Nico Pietroni, Daniele Panozzo, Olga Sorkine-Hornung, Enrico Puppo, and Paolo Cignoni. {\it Data-Driven Interactive Quadrangulation}. ACM Transactions on Graphics, 34(4) (proceedings of ACM SIGGRAPH), Article No.65, 2015.
\item {\bf Kenshi Takayama}, Daniele Panozzo, Olga Sorkine-Hornung. {\it Pattern-Based Quadrangulation for $N$-Sided Patches}. Computer Graphics Forum, 33(5) (proceedings of Eurographics Symposium on Geometry Processing), pp.177--184, 2014.
\item {\bf Kenshi Takayama}, Alec Jacobson, Ladislav Kavan, Olga Sorkine-Hornung. {\it A Simple Method for Correcting Facet Orientations in Polygon Meshes Based on Ray Casting}. Journal of Computer Graphics Techniques, 3(4), pp.53--63, 2014.
\item {\bf Kenshi Takayama}, Daniele Panozzo, Alexander Sorkine-Hornung, Olga Sorkine-Hornung. {\it Sketch-Based Generation and Editing of Quad Meshes}. ACM Transactions on Graphics, 32(4) (proceedings of ACM SIGGRAPH), Article No.97, 2013.
\item Nobuyuki Umetani, {\bf Kenshi Takayama}, Jun Mitani, Takeo Igarashi. {\it A Responsive Finite Element Method to Aid Interactive Geometric Modeling}. IEEE Computer Graphics and Applications, 31(5), pp.43--53, 2011.
\item {\bf Kenshi Takayama}, Ryan Schmidt, Karan Singh, Takeo Igarashi, Tamy Boubekeur, Olga Sorkine. {\it GeoBrush: Interactive Mesh Geometry Cloning}. Computer Graphics Forum, 30(2) (proceedings of Eurographics), pp.613--622, 2011.
\item {\bf Kenshi Takayama}, Olga Sorkine, Andrew Nealen, Takeo Igarashi. {\it Volumetric Modeling with Diffusion Surfaces}. ACM Transactions on Graphics, 29(6) (proceedings of ACM SIGGRAPH Asia), Article No.180, 2010.
\item Takashi Ijiri, {\bf Kenshi Takayama}, Hideo Yokota, Takeo Igarashi. {\it ProcDef: Local-to-global Deformation for Skeleton-free Character Animation}. Computer Graphics Forum, 28(7) (proceedings of Pacific Graphics), pp.1821--1828, 2009.
\item {\bf Kenshi Takayama}, Takashi Ashihara, Takashi Ijiri, Takeo Igarashi, Ryo Haraguchi, Kazuo Nakazawa. {\it A sketch-based interface for modeling myocardial fiber orientation that considers the layered structure of the ventricles}. The Journal of Physiological Sciences, 58(7), pp.487--492, 2008.
\item Takashi Ijiri, Takashi Ashihara, Takeshi Yamaguchi, {\bf Kenshi Takayama}, Takeo Igarashi, Tatsuo Shimada, Tsunetoyo Namba, Ryo Haraguchi, Kazuo Nakazawa. {\it A procedural method for modeling the Purkinje fibers of the heart}. The Journal of Physiological Sciences, 58(7), pp.481--486, 2008.
\item {\bf Kenshi Takayama}, Makoto Okabe, Takashi Ijiri, Takeo Igarashi. {\it Lapped Solid Textures: Filling a Model with Anisotropic Textures}. ACM Transactions on Graphics, 27(3) (proceedings of ACM SIGGRAPH), Article No.53, 2008.
\end{itemize}
